---
title: "Assignment1"
output:
  pdf_document: default
  html_document: default
---
###Data:

The data set is from Kaggle containing the McDonalds menu with nutrition information and some notes are available using R and python with plotly. Some demos in  (https://www.kaggle.com/limitpointinf0/mc-d-nutrition-eda ) and just keep a note for the talk https://github.com/jrauser/writing/blob/master/how_humans_see_data/hhsd_notes.Rmd 

I eat a lot of fast food and McDonalds is one of my most usually visit restaurant after midnight.
So I am very interested in how I gain so much weights, so this data set is fairly interesting to me.

###Graphs:
```{r, message=FALSE}
library(tidyverse)
library(ggplot2)
aa<-read.csv('menu.csv')
bb<-as_data_frame(aa)
```

Here, I have a question, why is that if I use read_csv('menu.csv'), this considers some categorigal data as char, so I have to use.function and change into dataframe. Can I have a way fixing it?

Graph 1:
```{r}
gg1<-ggplot(bb, aes(x=Category ,y=Calories, colour = Category)) +geom_boxplot()
gg1
```
This is very interesting for me that beverage has the least calories, I always thought the pop makes me fat.
```{r}
result <- bb %>% 
  select(Category,Item,Serving.Size,Calories) %>% group_by(Category) %>% top_n(3)# %>% summarise(Category,Calories)
data.frame(result[,c('Item','Calories')])
```
We can see from the select top 3 highest calories food from each Category, which is related with the size.

Graph 2:
```{r}
(gg2<-ggplot(bb,aes(x=Calories,y=Saturated.Fat,colour=Category))
+geom_point()+facet_wrap(~Category)+ geom_smooth(method='loess')+theme_minimal())
#scale_colour_hue(h = c(270, 360))+
gg2
```
From the second graph, we can tell that bad fat has postive linear correlation with calories, for beverages, salads and snacks \& Sides, the slopes are rather soft, which means that even though they have high calories, they do not contribute much to my fatness.

Therefore, sometimes high calories does not necessary means that it makes you fat, it depends on what kind of food you are taking.

Graph 3:
```{r}
(bb
  %>% group_by(Category,Calories.from.Fat,Calories)
  %>% summarise(prop=mean(Calories.from.Fat/Calories),
                n=n(),
                se=sqrt(prop*(1-prop)/n))
)->cc
(ggplot(cc,aes(Category,prop,colour=Category))+geom_jitter()
    +geom_linerange(aes(ymin=prop-se,ymax=prop+se)))
```
This graph shows the proportion of Calories from Fat for different kinds of food, we can tell that for different groups, we have barely the same proportion except for beverage, which is the lowest among all.